Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-11-12 manuscript/manuscript.tex
Fix editor's remark 12
Fix editor's remark 14
Fix editor's remark 16

On the first iteration, the ratio $L_r/L_r^\text{orig} = 1$ because the tesseroid being
divided is the original one.
For further iterations, the ratio will be progressively smaller than one as the
tesseroids get smaller.
This is intended to limit the number of divisions to the ones that will
significantly reduce the numerical error:
dividing a large tesseroid with a small $\text{max}\{ \Delta \rho(r') \}$ would
improve the integration accuracy more than dividing a small tesseroid with a
higher $\text{max}\{ \Delta \rho(r') \}$.
We also do not divide tesseroids with $L_r < 1$ mm because any integration errors would
be negligible due to the small mass of the tesseroid..

@@

\begin{equation}
    c = \frac{3300\text{kg/m$^3$} -
        2670\text{kg/m$^3$}}{R - R_1} R +
        2670\text{kg/m$^3$},
\end{equation}

@@

Having chosen values of $D$ equal to linear density case, we are free to explore the
integration error as a function of $\delta$ in more detail and how it varies for
different values of $b$ (Eq. \ref{eq:density-exp}).
We perform the error calculations for the ``Big Grid'' configuration (Table
\ref{tab:grids}) for two spherical shell models with 1km and 35km thickness.
The calculations are repeated for different values of $b$ to examine the error variation
with the sharpness of the density function.
Because larger $\delta$ values result in fewer tesseroid divisions,
our intention is to find the highest value of $\delta$ whose numerical error is bellow
the $0.1\%$ threshold.

>>>>

On the first iteration, the ratio $L_r/L_r^\text{orig} = 1$ because the tesseroid being
divided is the original one.
For further iterations, the ratio will be progressively smaller than one as the
tesseroids get smaller.
This is intended to limit the number of divisions to the ones that will
significantly reduce the numerical error:
dividing a large tesseroid with a small $\text{max}\{ \Delta \rho(r') \}$ would
improve the integration accuracy more than dividing a small tesseroid with a
higher $\text{max}\{ \Delta \rho(r') \}$.
We also do not divide tesseroids with $L_r < 1$ mm because any integration errors would
be negligible due to the small mass of the tesseroid.

@@

\begin{equation}
    b = \frac{3300\text{kg/m$^3$} -
        2670\text{kg/m$^3$}}{R - R_1} R +
        2670\text{kg/m$^3$},
\end{equation}

@@

Having chosen values of $D$ equal to the linear density case, we are free to explore the
integration error as a function of $\delta$ in more detail and how it varies for
different values of $b$ (Eq. \ref{eq:density-exp}).
We perform the error calculations for the ``Big Grid'' configuration (Table
\ref{tab:grids}) for two spherical shell models with 1km and 35km thickness.
The calculations are repeated for different values of $b$ to examine the error variation
with the sharpness of the density function.
Because larger $\delta$ values result in fewer tesseroid divisions,
our intention is to find the highest value of $\delta$ whose numerical error is bellow
the $0.1\%$ threshold.
